PAMELA: an annotation-based Java Modeling Framework

### 2021-04-21 ResponseLetterMinor.tex

 Title:    A LaTeX Template For Responses To a Referees' Reports
% Author:   Petr Zemek <s3rvac@gmail.com>
% Homepage: https://blog.petrzemek.net/2016/07/17/latex-template-for-responses-to-referees-reports/
% License:  CC BY 4.0 (https://creativecommons.org/licenses/by/4.0/)
\documentclass[10pt]{article}

@@

\NewDocumentCommand \ToolComments { m } {
  \section*{Tool~Comments~by~Reviewer~#1}
}

\ExplSyntaxOff
\AtBeginDocument{\maketitle\thispagestyle{empty}\noindent}

% You can get probably get rid of these definitions:
\newcommand\meta[1]{$\langle\hbox{#1}\rangle$}
\newcommand\PaperTitle[1]{``\textit{#1}''}

\title{Response letter to Manuscript SCICO-D-20-00176R1 entitled "PAMELA: an Annotation-Based Java Modeling Framework"}
%\author{Author1 \and Author2 \and Author3}
\date{\today}

@@

\begin{document}

Dear Editor,

\bigskip
Thanks for your message of Mars 15th, 2021, in which you suggested preparing a minor revision of our manuscript  \textbf{PAMELA: an Annotation-Based Java Modeling Framework}.

\bigskip
We are grateful to the reviewers for their interest, effort, and suggestions. We detail in the following pages how we have addressed the reviewers' concerns;  We have organized the responses to the comments on a per-reviewer basis, focusing, as suggested, on:

\begin{itemize}
\item Fixing typos, language errors, and other minor issues.
\item Refactoring Section 2.
\item Provide further explanations with respect to the performance of the approach.
\end{itemize}

@@

\bigskip
Sincerely yours,

\bigskip
Sylvain, Guillaume, Caine, Joel, Jean-Christophe, Salvador, Fabien and Antoine

\pagebreak

\Reviewer{\#1}
\begin{response}{There remain or are introduced however, a substantial number of typos, language errors, and other minor issues that need correcting:} 
All highlighted typos, languages errors and minor issues have been fixed.
\end{response}

@@

\pagebreak

\Reviewer{\#2}
\begin{response}{Would it be possible to structure it more, because currently it is several paragraphs the one bellow the others.}
We will probably do something...
\end{response}

\begin{response}{figure 2 is not enough described in section 2 and even in the paper.}
We have removed figure 2 ;) haha!
\end{response}

\begin{response}{More over, concerning section 4.4, I appreciate this new section. However, while reading, it is not a good advertisement for Pamela. Overhead (x20) is huge. Perhaps it is not the right benchmark if it provides bad results that are not representing the right usage.}
We totally agree...
\end{response}

\begin{response}{Minors}
We have fixed all the highlighted minor issues.
\end{response}

### 2021-04-21 1-Main.tex
fix compilation warnings
typos
Adding response letter template
ad package siunitx
Updates from Overleaf
Adding minor revision response letter

\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tikz-uml}

@@

% DRAFT
\newcommand{\ab}[1]{{\color{blue} #1}} % draft mode

@@

@@

\address[mymainaddress]{ENSTA Bretagne, Lab-STICC, UMR 6285, Brest, France}%vérifier si c'est l'affiliation officielle
\address[mysecondaryaddress]{IMT Atlantique, Lab-STICC, UMR 6285, F-29238 Brest, France}

>>>>

\usepackage{listings}
\usepackage{xcolor}
\usepackage{siunitx}
\usepackage{tikz-uml}
\usepackage{hyperref}
\hypersetup{pdfauthor={Sylvain Guérin, Jean-Christophe Bach, Antoine Beugnard, Joel Champeau, Salvador Mart\'inez, Guillaume Pollet, Caine Silva}}

@@

% DRAFT
\newcommand{\ab}[1]{{\color{blue} #1}} % draft mode
\newcommand{\jcb}[1]{{\color{red} #1}} % draft mode
\newcommand{\sg}[1]{{\color{purple} #1}} % draft mode

@@

\author[mysecondaryaddress]{Fabien Dagnat}
%\ead{firstname.lastname@imt-atlantique.fr}

@@

\address[mymainaddress]{ENSTA Bretagne, Lab-STICC, UMR 6285, Brest, France}%vérifier si c'est l'affiliation officielle
\address[mysecondaryaddress]{IMT Atlantique, Lab-STICC, UMR 6285, Brest, France}

### 2021-04-21 introduction.tex
Adding minor revision response letter

Conversely, we propose a shift in the modeling paradigm in which models and code are developed together and at the same time in what we call a continuous modeling process. The PAMELA framework supports this paradigm shift by providing the means to: 1) annotate Java code with model-based annotations; and 2) interpret these annotations at runtime.

>>>>

Conversely, we propose a shift in the modeling paradigm in which models and code are developed together and at the same time in what we call a continuous modeling process. The PAMELA framework supports this paradigm shift by providing the means to: 
% Joel 1) annotate Java code with model-based annotations; 
%and 2) interpret these annotations at runtime.
1) weave model-based annotations with Java source code
and 2) interpret model annotations at run-time.
